%==========================================================
%======================  FRONT STUFF ======================
%==========================================================

%======================= Cover Page =======================
\newpage
%\begin{document}
\pagestyle{plain}
%\pagenumbering{roman}
\setcounter{page}{1}
\addcontentsline{toc}{section}{Title Page}
%\setlength{\footskip}{-15mm}
\setlength{\textheight}{230mm}
\setlength{\voffset}{10mm}
\vskip -5em

\begin{center}
{ 
  \singlespace \uppercase{\bf Deep Learning For Face Recognition in Surveillance Videos} \par
}
\vskip 2em
{
  \lineskip 1.5em
  \begin{tabular}[t]{c} by\\ \\ Paul-Darius Sarmadi
  \end{tabular}\par
}
%\vskip 5.6em

\vskip 3.5em
\singlespace A dissertation submitted in partial fulfillment of the
requirements for the degree of\\ Master of Science in\\ Computer Science 

%	\vskip 5em
\vskip 0.5em
{
  \singlespace
  \begin{center}
    \begin{tabular}{rl}
      \\[-1em]
      Examination Committee: & Dr.\ Matthew Dailey (Chairperson) \\[-0.8em]
                             & Dr.\ Mongkol Ekpanyapong \\[-0.8em]
                             & Prof.\ Manukid Parnichkun \\\\

% UNCOMMENT THE LINES BELOW IF YOU HAVE THE EXTERNAL EXAMINER.
%      External Examiner:     & Prof.\ YOUR EXTERNAL EXAMINER \\[-0.8em]
%                             & Dept.\ of Electrical and Computer Engineering \\[-0.8em]
%                             & McGill University, Canada \\\\
		
      Nationality:     & French \\[-0.8em]
      Previous Degree: & Bachelor of Science in Math, Physics\\[-0.8em]
                       & TELECOM SudParis, France\\[-0.8em]
      \\
      Scholarship Donor: & Telecom SudParis, France - AIT\\[-0.8em]
    \end{tabular}
  \end{center}

  \vskip 3.0em
  \centerline{}
  \vskip 2em
}
\end{center}
\begin{center}
  \singlespace Asian Institute of Technology\\ School of Engineering
                  and Technology\\ Thailand\\ May 2016
\end{center}
\vfill

%====================== ACKNOWLEDGEMENTS ======================
\newpage
\pagestyle{plain}
\addcontentsline{toc}{section}{Acknowledgments}
\onecolumn % Single-column.
\if@twoside\else\raggedbottom\fi % Ragged bottom unless twoside option.
\setlength{\footskip}{8mm}
\begin{center}
{
  \large \bf Acknowledgments\\ \vskip 1em
}
\vskip 1em
\end{center}
\singlespace
\doublespace
\hspace{8.5mm}
\vspace{-1em}

I want to thank my advisor Dr. Matthew Dailey for his precious help during this research work and all the committee members for their advice and remarks.\\

I also want to thank my family for all they brought me.\\

In particular, I want to thank my little brother Maximilien and my little sister Melanie. It is for them that I work and it is thank to them that I smile.


%====================== ABSTRACT ======================
\newpage
\pagestyle{plain}
\addcontentsline{toc}{section}{Abstract}
\onecolumn % Single-column.
\if@twoside\else\raggedbottom\fi % Ragged bottom unless twoside option.

\setlength{\footskip}{8mm}

\begin{center}
{\large \bf Abstract \\ \vskip 1em}
\vskip 1em
\end{center}
\singlespace
\doublespace
\hspace{8.5mm}
\vspace{-1em}


The problem of recognizing a previously identified criminal, hoping to follow him or her through video cameras feeds is a key issue. However, police require a great deal of human resources to perform this task. Automating the face verification process in surveillance video seems to be a feasible solution to this problem. Deep learning algorithms have recently reached particularly high levels of accuracy in automated face verification. For example, recent approaches reached over 98\% accuracy on the \enquote{Labeled Faces in the Wild} (LFW) database. The goal of this research is to explore the possibility of adapting such methods to the particular conditions and constraints of video surveillance. I performed experiments on a database of surveillance videos acquired in a crowded shopping mall. With the neural network architecture described in this article, an accuracy of 88.04\% was reached on the database.\\

Keywords: face verification, surveillance video, deep learning, deep neural network, convolutional neural network.


\setlength{\parskip}{0pt} 
%======================= Table of Contents =========================
\newpage
\addcontentsline{toc}{section}{Table of Contents}
\tableofcontents

% Page 2 begins

%===================== List of Figures ======================
\newpage
\addcontentsline{toc}{section}{List of Figures}
\listoffigures

%\clearpage     % \clearpage ends the page, and also dumps out all floats.
%\end{document} % Floats are things like tables and figures.

%\clearpage     % \clearpage ends the page, and also dumps out all floats.

% %===================== List of Tables ======================
%\newpage
%\addcontentsline{toc}{section}{List of Tables}
%\listoftables

% %\clearpage     % \clearpage ends the page, and also dumps out all floats.
% %\end{document} % Floats are things like tables and figures.

%\clearpage     % \clearpage ends the page, and also dumps out all floats.

\setlength{\parskip}{12pt}