\setlength{\footskip}{8mm}

\chapter{Preliminary Results}
\label{ch:results}

Before the proposal, some parts of the solution have been built.
\begin{itemize}
\item Scripts to generate the database of face images from a video surveillance sequence have been written. The database has been generated and is usable for a direct face identification model. However, the overlap calculation for face detection is not written yet. Hence, the number of available classes is limited, decreasing the performances of a \enquote{Same/Not Same} network. The direct face identification model is not be affected by this issue, however it can be built with the current version of the database. The database contains 55,203 images. After manual labeling of the faces in the database, 183 images were labeled 1 for the first researcher, 325 were labeled 2, 15 were labeled 3.
\item The scripts to generate the database files mentioned in Figure 3.2 are fully written, and work both for a direct face identification and for a Siamese network. They were executed for this second scenario. Four files \enquote{train1.txt}, \enquote{train2.txt}, \enquote{test1.txt}, and \enquote{test2.txt}, as described in section 3.6.2, were built.
\item A Siamese model has been designed with Caffe and was trained on the generated database for 50,000 epochs. This training took a night, with batches of size 20, on the 780 GTX GPU card given by the laboratory. The accuracy of the resulting network could not be tested yet because of the singular output generated by such a network, as mentioned in section 2.3.1. A script is being written to face this issue.
\end{itemize}

\FloatBarrier

